Notes on Semi-Supervised `Novelty Detection'

### 2011-04-05 semisupervised/notes.tex
Started scripts to pretty print results directly form python to LaTeX.

\section{Experiment}
\label{sec:experiment}

>>>>

\section{Experiment - Simple}

\note{This first experience is very small and was only used to better explain the effects of the threshold functions.}

For a better understanding of how the knowledge of the unconditional probability $P(x)$ can help to improve the detection threshold
a very small toy experiment was run:

The detection system is given access to labelled data ($known = \{kitchen, corridor\}$)
filtered from the distribution described in \autoref{tab:simple-distribution} as well to unlabelled samples from it.
From that input it learns both $P(x)$ and $P(x|class \in known)$.
Later the whole input space is sorted by the diferent thresholds for analysis.

Since the input space is very small (6 possible inputs), simple accumulation tables where used to learn both distributions.

\begin{table}[h]
\begin{center}
\input{simple-data/explain}
\end{center}
\caption{\label{tab:simple-distribution}Distribution used on the simple experiment.}
\end{table}

\begin{table}[h]
\begin{center}

\begin{tabular}{ |c| |c|}
\hline
$P(x|class \in know)$ & $\frac{P(x|class \in know)}{P(x)}$ \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
\end{tabular}

\end{center}
\caption{\label{tab:simple-threshold}Input space sorted by threshold.}
\end{table}
\section{Experiment}
\label{sec:experiment}
